### 2023-01-24 Strydom_et_al_2023_graph_embedding_preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@32377dfbc750a8864f2ea754d587f4308f4fb1f0 🚀

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

@@

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Graph embedding and transfer learning can help
predict species interaction networks despite data limitations}
\vskip 5em

%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,2,3}\quad %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{2,5}\quad %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{7}\quad %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{2,3}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{2,5}\quad %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{8}\quad %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{9}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}

\textsuperscript{1}\,Département de Sciences Biologiques, Université de
Montréal, Montréal, Canada\quad \textsuperscript{2}\,Quebec Centre for
Biodiversity Science, Montréal,
Canada\quad \textsuperscript{3}\,Département de Biologie, Université de
Sherbrooke, Sherbrooke, Canada\quad \textsuperscript{4}\,Department of
Forest Resources Management, University of British Columbia, Vancouver,
B.C., Canada\quad \textsuperscript{5}\,Department of Biology, McGill
University, Montréal, Canada\quad \textsuperscript{6}\,Department of
Ecology \& Evolutionary Biology, University of Toronto, Toronto,
Canada\quad \textsuperscript{7}\,Department of Forest and Conservation
Sciences, University of British Columbia, Vancouver,
Canada\quad \textsuperscript{8}\,Centre for Integrative Ecology, School
of Biological Sciences, University of Canterbury, Canterbury, New
Zealand\quad \textsuperscript{9}\,School of Mathematics and Statistics,
University of Canterbury, Canterbury, New Zealand

\textsuperscript{‡}\,Equal contributions\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill

@@

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

>>>>

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}

\geometry{includemp,
            letterpaper,
            top=2.4cm,
            bottom=2.4cm,
            left=1.0cm,
            right=1.0cm,
            marginparwidth=5cm,
            marginparsep=1.0cm}

\usepackage[singlelinecheck=off]{caption}

\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}

\usepackage{floatrow}

\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}

% \floatsetup[table]{margins=hangright,
%              facing=no,
%              capposition=beside,
%              capbesideposition={center,outside},
%              floatwidth=\textwidth}

@@

\setcounter{secnumdepth}{5}

\usepackage{titlesec}

\titleformat{\section}[block]
{\normalfont\large\sffamily}
{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}

\titleformat{\subsection}[runin]
{\normalfont\fontseries{b}\selectfont\filright\sffamily}
{\thesubsection.}{.5em}{}

\titleformat{\subsubsection}[runin]
{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}

\fancypagestyle{firstpage}
{
   \fancyhf{}
   \renewcommand{\headrulewidth}{0pt}
   \fancyfoot[R]{\footnotesize\ccby}
   \fancyfoot[L]{\footnotesize\sffamily\today}
}

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}

\usepackage{tikz}
\begin{document}
\tikz [remember picture, overlay] %
\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
\pagestyle{normal}
\thispagestyle{firstpage}

\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}

\noindent {\LARGE \textbf{\textsf{Graph embedding and transfer learning
can help predict species interaction networks despite data
limitations}}}

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}, %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,2,3}, %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}, %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{2,5}, %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}, %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{7}, %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{2,3}, %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{2,5}, %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{8}, %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{9}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}
\vskip 1em
\textsuperscript{1}\,Département de Sciences Biologiques, Université de
Montréal, Montréal, Canada; \textsuperscript{2}\,Quebec Centre for
Biodiversity Science, Montréal, Canada; \textsuperscript{3}\,Département
de Biologie, Université de Sherbrooke, Sherbrooke,
Canada; \textsuperscript{4}\,Department of Forest Resources Management,
University of British Columbia, Vancouver, B.C.,
Canada; \textsuperscript{5}\,Department of Biology, McGill University,
Montréal, Canada; \textsuperscript{6}\,Department of Ecology \&
Evolutionary Biology, University of Toronto, Toronto,
Canada; \textsuperscript{7}\,Department of Forest and Conservation
Sciences, University of British Columbia, Vancouver,
Canada; \textsuperscript{8}\,Centre for Integrative Ecology, School of
Biological Sciences, University of Canterbury, Canterbury, New
Zealand; \textsuperscript{9}\,School of Mathematics and Statistics,
University of Canterbury, Canterbury, New Zealand\\
\textsuperscript{‡}\,Equal contributions\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
\noindent

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
ecological networks\\network embedding\\transfer learning\\network
macroecology\\}
}

@@

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
